\chapter*{ABSTRACT}

\noindent System on a Chip (SoC) is an embedded system module
Has a certain functionality in a silicon chip board that can also be called
With Veri Large Scale Integration (VLSI). The owner of the SoC design has
Copyright over the system design that has been created. Fabless manufacturing is
How to mold a hardware module that is designer Integrated Circuit (IC)
Is Outsourching from outside the printing factory.

\vspace*{0.5cm}
\noindent Fabless manufacturing from IC design has gap design theft
When the design will be printed or when the project requires mutiple module
With various functions from various designers. Therefore every module is VLSI
From this chip designer requires proof of ownership from the designer or
Production company. In this study writer make a verification of ownership design
with 2 dedicated verification keys ie Polygate as the primary key going
Activate the second key, and the second key will be active which process
Using a digital filter algorithm.

\vspace*{0.5cm}
\noindent Security uses the Obfuscation algorithm to protect the main circuit. The main circuit is inserted with a protective circuit without altering and disrupting the main function of the circuit. The Obfuscation technique is performed on the behavioral level and synthesis level. In the compilation of synthesis design (RTL) obtained main circuit and protector mixed into one. So in the final design as there, it look like is no other circuit other than the main circuit. And if the circuit is successfully cloned then the circuit can be claimed by using a special tool to activate the protective circuit.

\vspace*{0.5cm}

\noindent \textbf{Keywords}: VLSI, Intellectual Property Protection, Digital Signal Processing, Polygate Watermark.

\newpage